### 2020-12-10 doc/manuscript/Dow_manuscript_Nature.Rmd
update

#Table numbers
hypothesis_table=1
table_species=2  #goes to SI
mean_growth_parameters_table=3

@@

(*most of this is too detailed for Nature*)

>>>>

#Table numbers
hypothesis_table=1
table_species=2  #goes to SI
mean_growth_parameters_table=3  #probably goes to SI

@@

(*most or all of this should be cut-- first paragraph too detailed for Nature, and we want minimal comparison of ring vs diffuse porous*)
